Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex
updated citations

	\section{Algorithms}
	 Part of speech tagging and bigram models
 	 Use for subset of data that has high predictability
 	 Supervised LSA for the rest of the data

 	 Other methods had low accuracy 
 	\subsection{Part-of-Speech}
 	\subsection{Semantic Knowledgebase}
	\subsection{Supervised LSA}
	Our approach uses simple LSA with a supervised learning component.

>>>>

	\section{Algorithms}
	 Our approach was essentially a pipeline of different sorts of models. 
	 The first stage consisted of part-of-speech tagging and bigram models, which
	 was used for the subset of data that had high predictability. 
	 Originally, we implemented a step that included knowledge-base approaches like
	 semantic similarity, but later discarded it from the pipeline because its accuracy
	 was not very good.

	 For the rest of the data, we implemented a Supervised LSA approach, which was to
	 an extent a novel approach.

	 We detail the methods in the following sections. 
 	\subsection{Part-of-Speech}
 	\subsection{Semantic Knowledgebase}
	\subsection{Supervised LSA}
	Our approach uses simple LSA with a supervised learning component.
